Label object representation and manipulation with ITK

### 2007-10-08 article/Article.tex
a few words about the removed UseBackground feature
darcs-hash:20071008075908-2fc9d-a1bc1709f2acd93b2167f8bdc1293bb16b7c1ba4.gz

The {\em itk::LabelMap} class is in charge of managing the
collection of label
objects of the image, as well as storing the metadata associated with the image
like
the spacing, the physical position - all the metadata found in {\em itk::Image}.

>>>>

The {\em itk::LabelMap} class is in charge of managing the collection of label
objects of the image, as well as storing the metadata associated with the image
like the spacing, the physical position - all the metadata found in {\em
itk::Image}. It has been chosen, to simplify the implementation and the tests,
and because the feature is rarely useful in practice, to not implement the
conditional background in the {\em itk::LabelMap} class\footnote{The classes
before the {\em revision 4} were implemented with the conditional background
feature. All the related code has been removed bitween revision 3 and revision
4.}. All the images represented by a {\em itk::LabelMap} object have a
background. If the user want to manipulate such an image with no background,
he/she has to avoid the background label, for example by using a larger label
type.
